DeepFovea++: Reconstruction and Super-Resolution for Natural Foveated Rendered Videos

### 2020-07-16 DeepFovea++ paper/paper.tex
Add new version of the paper

\begin{multline} \label{eq:loss}
    \mathcal{L}=w_{\text{sv}}\,\mathcal{L}_{\text{sv}} + w_{\text{adv}}\,\mathcal{L}_{\text{adv}} + w_{\text{adv fft}}\,\mathcal{L}_{\text{adv fft}}\\
    + w_{\text{flow}}\,\mathcal{L}_{\text{flow}} + w_{\text{LPIPS}}\,\mathcal{L}_{\text{LPIPS}}    
\end{multline}

For the supervised loss $\mathcal{L}_{\text{sv}}$ we used the general and adaptive robust loss function introduced in \ref{subsec:generaladaptierobustloss}.\cite{adaptiveroubustloss} \\
The adversarial loss functions $\mathcal{L}_{\text{adv}}$ and $\mathcal{L}_{\text{adv fft}}$ represents the non-saturating generator GAN loss, which is defined as: \cite{gan}

@@

We take the outputs of the second convolution of the first five blocks of a pre-trained VGG-19 to compute the perceptual loss. This choice is inspired by the original DeepFovea framework. \cite{vgg, deepfovea}

@@

\vfill

>>>>

	\begin{multline} \label{eq:loss}
		\mathcal{L}=w_{\text{sv}}\,\mathcal{L}_{\text{sv}} + w_{\text{flow}}\,\mathcal{L}_{\text{flow}} + w_{\text{adv}}\,\mathcal{L}_{\text{adv}} + w_{\text{adv fft}}\,\mathcal{L}_{\text{adv fft}}\\
		+ w_{\text{flow}}\,\mathcal{L}_{\text{flow}} + w_{\text{LPIPS}}\,\mathcal{L}_{\text{LPIPS}}    
	\end{multline}

	For the supervised loss $\mathcal{L}_{\text{sv}}$ we used the general and adaptive robust loss function introduced in \ref{subsec:generaladaptierobustloss}.\cite{adaptiveroubustloss}\\
	The adversarial loss functions $\mathcal{L}_{\text{adv}}$ and $\mathcal{L}_{\text{adv fft}}$ represents the non-saturating generator GAN loss, which is defined as: \cite{gan}

@@

	We take the outputs of the second convolution of the first five blocks of a pre-trained VGG-19 to compute the perceptual loss. This choice is inspired by the original DeepFovea framework. \cite{vgg, deepfovea}\\
	To achieve consistency across frames we also utilized a flow loss $\mathcal{L}_{flow}$. This flow loss is defined as the L1 loss between one predicted frame and the corresponding backward wrapped subsequent frame. To be able to perform the backward wrapping operation we computed the optical flow between the two relevant frames by utilizing a pre-trained PWC-Net. \cite{deepfovea, pwcnet}

@@
